---
title: "pml"
author: "anoushka"
date: "18/10/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#question
Analysis of a data set.


#Load the data

```{r, results=FALSE}
library(caret)
library(Hmisc)
library(corrplot)
library(e1071)
library(randomForest)
```


```{r}
set.seed(3566)
download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv",
              destfile = "./training.csv", 
              method = "curl")

download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv",
              destfile = "./testing.csv", 
              method = "curl")
```



```{r}
train1 = read.csv("training.csv")
test1 = read.csv("testing.csv")
```
Next step is to find any missing values and clean the data.

```{r}
set.seed(3566)
summary(train1)
```
```{r}
set.seed(3566)
train = read.csv("training.csv", na.strings=c("#DIV/0!"))
train2 <- nearZeroVar(train)
train<-train[ , -train2]
variables <- colnames(train[colSums(is.na(train)) == 0])
d<- train[variables]
wd <- d[ , -(1:6)]
dim(wd)
```

#Splitting the dataset
We now proceed to splitting our dataset into testing and training. Testing=0.75% and training=0.25%
We also find correlation between attributes.


```{r}
set.seed(3566)
Train3 <- createDataPartition(y=wd$classe, p=0.75, list=FALSE )
Trainingdata_sub <- wd[Train3,]
Testingdata_sub <- wd[-Train3,]
Q <- cor(Trainingdata_sub[ , -53])
corrplot(Q, order = "FPC", method = "square")
```

We observe the correlation between all the attributes of the dataset to find hidden patterns.


#Finding hidden patterns

We need to plot the confusion matrix to find the true positives, false positives, true negatives and the false negatives.

1. SVM:


```{r}
set.seed(3566)
SVM1 <- svm(classe ~ ., data = Trainingdata_sub)
SVMPredict <- predict(SVM1, newdata = Testingdata_sub)
confusionMatrix(SVMPredict, Testingdata_sub$classe)
```



##The svm aka support vector machine model gave the accuracy 94.09%. This is a good model.


